A Fiber Collision Correction Method for the BOSS Power Spectrum

### 2015-04-16 fc_paper/fc_paper.tex
First edits after Mike's comments
No substance change yet.

\title{Fiber Collision Correction Method for BOSS Power Spectrum}

\author{ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
Roman~Scoccimarro\altaffilmark{1}} 
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}

\begin{abstract}
Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies. However the physical size of fibers limit these surveys from successfully collecting redshifts from galaxies that are within the angular fiber-collision scale of one another, which ultimately lead to significant systematic effects on galaxy clustering measurements. Using simulated mock catalogues, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber-collisions in the literature and assess their success in reconstructing the true power spectrum.

We present our fiber-collision correction method, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we successfully reproduce the true power spectrum for the mock catalogues with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$. Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data. With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allows us constrain a main contributor to systematic effects and extend power spectrum measurements to smaller scales. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

\section{Introduction} 
Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.

For each galaxy, a fiber is used to obtain a spectroscopic redshift. However, due to the physical size of the fibers even with efficient targeting strategies (e.g. \citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to separately extract the spectroscopic information (\citealt{Yoon:2008aa} {\bf CITE MORE}). In these situations, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured. With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.

As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe as the fiber-collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales. SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$. This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}). Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and must be understood as these measurements probe to smaller scales and as higher order statistics such as the three-point correlation function or the bispectrum are used in cosmological studies. Perhaps with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) will render fiber-collisions obsolete. However, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.

To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}). For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor. This provides a reasonable correction for the fiber-collision effects at scales much larger than the fiber-collision scales; however the correction falls short near the fiber-collision scale. In fact, as \cite{Zehavi:2005aa} find, fiber-collisions affect the two-point correlation function (2PCF) measurements even on scales significantly larger than the fiber-collision scale ( $> 1\;\mathrm{Mpc}/h$). For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber-collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}). While this shot-noise term adjustment has been calibrated within the mock catalogues used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations. Methods of this kind rely entirely on the accuracy of the mock catalogues to constrain fiber-collisions, which is especially concerning since fiber-collisions systematically affect small scales and mock catalogues may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).

Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber-collision correction method for the 2PCF that is able to reasonably correct for fiber-collisions above and below the collision scale. \cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber-collisions. Unfortunately, this method cannot be applied to the Fourier clustering measurements due to the complex geometry of the overlapping regions. As a result, we propose a fiber-collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber-collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.

In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogues with realistically applied fiber-collisions and the power spectrum estimator used throughout the paper. Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber-collisions of power spectrum measurements and test and compare correction methods in the literature. Afterwards, we present our correction method, test it on the mock catalogues, and compare it to other correction methods in Section \ref{sec:results}. Finally in Section \ref{sec:summary} we summarize and discuss our results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogues play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Guo:2012aa, Manera:2013aa} {\bf LIST MORE}) since systematic effects can be simulated on the mock catalogues. This allows us to test how these effects influence clustering measurements and devise correction methods that attempt to account for these effects.

A direct way of understanding the effects of fiber-collisions on clustering statistics in observations is to first apply fiber-collisions to mock catalogues then compare the clustering statistics obtained from mock catalogues with and without the fiber collisions. Correction methods for fiber-collisions can then be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogues without fiber-collisions. The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber-collisions and improves the clustering measurements.

When applying the fiber-collisions to the mock catalogues, it is essential to apply them in the same manner they affect the observational data. For BOSS, galaxies within $62"$ are fiber-collided (\citealt{Anderson:2012aa}). In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber-collision angular scale (\citealt{Guo:2012aa}). Furthermore, fiber-collisions are only one of the systematic effects that influence BOSS data. Systematic effects include the unique geometry of the BOSS survey, the variable completeness in different sectors of the survey, and redshift failures (\citealt{Anderson:2012aa}).

\def \cmasscolor{black}
\def \ldgcolor{blue}
\def \qpmcolor{orange}
\def \tmcolor{green}
\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues. The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor). Bin size of $\Delta z = 0.025$ was used to compute the each of the distributions. LasDamas mock catalogue has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample. QPM and Tiling Mock catalogues, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure}

Effects of fiber-collisions must be understood and interpreted in conjunction with these other systematic effects. Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions. Therefore they provide complementary data sets to measure the effects of fiber-collisions and to test our correction method tailored for BOSS. 
%Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies". % Include brief detail on what each mock has to offer

The LasDamas Galaxy mock catalogues is constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$. The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation. The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa, McBride:2011aa}). The HOD prescription is specified so that the galaxy mock catalogues reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$. The LasDamas galaxy mock catalogues have 40 realizations that spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7. They also include redshift space distortions from velocities, but do not model fiber-collisions.

To model the fiber-collisions of the observed galaxies in BOSS, we impose fiber-collisions at the angular scale of $62''$. Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it. Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogues are affected by fiber-collisions.

Next, the QPM mock galaxy catalogues uses a ``quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume. The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations. Afterward the \cite{Tinker:2012aa} HOD parameterization is used to populate the halos. The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsamped based on angular sky completeness (sector completeness) and radial selection. Furthermore, QPM mocks model the fiber-collisions of the BOSS CMASS sample ($62''$ angular fiber-collision scale). The QPM galaxy mock catalogue uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$. We use 1000 realizations of the QPM galaxy mock catalogue. For a detailed description of the QPM galaxy mock catalogues we refer readers to \cite{White:2014aa}.

Finally the Tiling Mock catalogue is generated using

@@

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies. The LasDamas mock catalogue, which is constructed based on the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).

\subsection{Power Spectrum Estimator} \label{sec:pk_est}
In this paper, we focus on the effects of fiber-collisions on the galaxy power spectrum out of the other clustering measurements. Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper: 
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator. The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogues. We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement. We remind readers that the LasDamas mock catalogue has an overall greater $\overline{P(k)}$ due to the fact that the catalogue spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogues.} \label{fig:mockpk}
\end{center}
\end{figure}

For LasDamas, QPM, and Tiling mock catalogues we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}. The fiber-collisions described previously are not applied to the mock catalogues in the $P(k)$ calculations for Figure \ref{fig:mockpk}. Without fiber-collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.

>>>>

\title{A Fiber Collision Correction Method for the BOSS Power Spectrum}

\author{ChangHoon~Hahn\altaffilmark{1}, 
Roman~Scoccimarro\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, others} 
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}

\begin{abstract}
Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies. However physical constraints limit these surveys from successfully collecting redshifts from galaxies that are too close to each other on the focal plane, which ultimately leads to significant systematic effects on galaxy clustering measurements. Using simulated mock catalogs, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber collisions in the literature and assess their success in reconstructing the true power spectrum.

We present our fiber collision correction method, which first statistically reconstructs the clustering of fiber collided pairs by modeling the distribution of the line-of-sight displacements between them using cases where both redshifts are obtained. The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we successfully reproduce the true power spectrum for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$. Our comparisons to other existing correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data. With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allow us to extend power spectrum measurements to smaller scales than previously possible. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

\section{Introduction} 
As of 2015, millions of redshifts to distant galaxies have been obtained through redshift surveys. Cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.

For each galaxy, a fiber is used to obtain a spectroscopic redshift. However, due to the physical size of the fiber housing, if two galaxies are located within the fiber collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to observe them simultaneously (\citealt{Yoon:2008aa} {\bf CITE MORE}). In these situations, only a single redshift is measured. With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.

As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales. SDSS-III BOSS, in particular, has an angular fiber collision scale of $62''$. This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}). Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant. They must to be accounted for to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum. Even with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) 
% What is the fiber positioner areas called??
will render fiber collisions obsolete. Therefore, accounting for the systematic effects remains an unavoidable challenge for clustering statistics.

To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}). For fiber collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber collided galaxy to its nearest angular neighbor. This provides a reasonable correction for the fiber collision effects at scales much larger than the fiber collision scales; however the correction falls short near the fiber collision scale. In fact, as \cite{Zehavi:2005aa} find, fiber collisions affect the two-point correlation function (2PCF) measurements even on scales significantly larger than the fiber collision scale ( $> 1\;\mathrm{Mpc}/h$). For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}). While this shot-noise term adjustment has been calibrated within the mock catalogs used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations. Methods of this kind rely entirely on the accuracy of the mock catalogs to constrain fiber collisions, which is especially concerning since fiber collisions systematically affect small scales and mock catalogs may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).

Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber collision correction method for the 2PCF that is able to reasonably correct for fiber collisions above and below the collision scale. \cite{Guo:2012aa} estimates the total contribution of fiber collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber collisions. Unfortunately, due to the complex geometry of the overlapping regions, this method is difficult to apply to Fourier clustering measurements. As a result, we propose a fiber collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber collided galaxies to statistically reconstruct the clustering of fiber collided galaxies; and properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.

In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper. Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber collisions of power spectrum measurements and test and compare correction methods in the literature. Afterwards, we present our correction method, test it on the mock catalogs, and compare it to other correction methods in Section \ref{sec:results}. Finally in Section \ref{sec:summary} we summarize and discuss our results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% fiber collided Mock catalogs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{fiber collided Mock catalogs} \label{sec:catalog}
For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogs play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber collisions (\citealt{Guo:2012aa, Manera:2013aa} {\bf LIST MORE}) since systematic effects can be simulated on the mock catalogs. This allows us to test how these effects influence clustering measurements and devise correction methods that attempt to account for these effects.

A direct way of understanding the effects of fiber collisions on clustering statistics in observations is to first apply fiber collisions to mock catalogs and then compare the clustering statistics obtained from mock catalogs with and without the fiber collisions. Correction methods for fiber collisions can then be applied to the fiber collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogs without fiber collisions. The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber collisions and improves the clustering measurements.

When applying the fiber collisions to the mock catalogs, it is essential to apply them in the same manner they affect the observational data. For BOSS, galaxies within $62"$ are fiber collided (\citealt{Anderson:2012aa}). In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber collision angular scale (\citealt{Guo:2012aa}). Furthermore, fiber collisions are only one of the systematic effects that influence BOSS data. Systematic effects include the unique geometry of the BOSS survey, the variable completeness in different sectors of the survey, and redshift failures (\citealt{Anderson:2012aa}).

\def \cmasscolor{black}
\def \ldgcolor{blue}
\def \qpmcolor{orange}
\def \tmcolor{green}
\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor). Bin size of $\Delta z = 0.025$ was used to compute the each of the distributions. LasDamas mock catalog has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample. QPM and Tiling Mock catalogs, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure}

Effects of fiber collisions must be understood and interpreted in conjunction with these other systematic effects. Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogs ({\bf CITATIONS?}), which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions. Therefore they provide unique data sets to measure the effects of fiber collisions and to test our correction method tailored for BOSS. 
%Each of these mock catalogs use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies". % Include brief detail on what each mock has to offer

The LasDamas Galaxy mock catalogs are constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$. The N-body LasDamas simulations use a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation. The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogs (\citealt{McBride:2009aa, McBride:2011aa}). The HOD prescription is specified so that the galaxy mock catalogs reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$. The LasDamas galaxy mock catalogs have 40 realizations, each of which spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7. They also include redshift space distortions from velocities, but do not model fiber collisions.

To model the fiber collisions of the observed galaxies in BOSS, we impose fiber collisions at the angular scale of $62''$. Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it. Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogs are affected by fiber collisions.

Next, the QPM mock galaxy catalogs uses a ``quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume. The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations. Afterward the \cite{Tinker:2012aa} HOD parameterization is used to populate the halos. The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsampled based on angular sky completeness (sector completeness) and radial selection. Furthermore, QPM mocks model the fiber collisions of the BOSS CMASS sample ($62''$ angular fiber collision scale). The QPM galaxy mock catalog uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$. We use 1000 realizations of the QPM galaxy mock catalog. For a detailed description of the QPM galaxy mock catalogs we refer readers to \cite{White:2014aa}.

Finally the Tiling Mock catalog is generated using

@@

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogs along with the redshift distribution of BOSS DR12 galaxies. The LasDamas mock catalog, which is constructed based on the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).

\subsection{Power Spectrum Estimator} \label{sec:pk_est}
In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements. Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper: 
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalog, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator. The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogs. We emphasize that fiber collisions were not applied to the mock catalogs for the $P(k)$ measurements. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement. We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
\end{center}
\end{figure}

For LasDamas, QPM, and Tiling mock catalogs we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}. The fiber collisions described previously are not applied to the mock catalogs in the $P(k)$ calculations for Figure \ref{fig:mockpk}. Without fiber collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.

We also plot the $P(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}. For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber collisions. Each galaxy has a statistical weight determined by, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation} 
(\citealt{Anderson:2012aa, Beutler:2014aa}). As a result, we modify Equation \ref{eq:fkppk} when we calculate the power spectrum. Instead of the galaxy density term $n_g({\bf r})$ we use a weighted galaxy density term $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$, which includes the systematic weights for each galaxy. Also, instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.
